\titel

### 2014-03-09 presentation/presa.tex
Adding slide about HRFF, which the RFF authors promise in future work

  \includegraphics[width=\textwidth]{images/rff-results.pdf}

@@

\begin{frame}
  \frametitle{Planning under uncertainty: FF-Replan vs. RFF}
\end{frame}

>>>>

  \includegraphics[width=\textwidth]{images/rff-results.pdf}
\end{frame}

\begin{frame}
  \frametitle{RFF Discussion}

  \begin{itemize}
    \item Won the IPC-08 competition in the ``Fully Observable Probabilistic'' track
    \item Probability a sulution is found is $1 - \rho$
    \item $> \rho$ means more replanning
  \end{itemize}

  \setbeamertemplate{itemize items}[square]
  \begin{itemize}
    \item A clear goal must be defined. Does not perform well for the Search-and-Resque domain
    \item
  \end{itemize}

@@

\begin{frame}
  \frametitle{After RFF}

  \begin{itemize}
    \item In the ``Future Work'' the authors promised to generalize to Hybrid MDPs
    \item \emph{``Fast Incremental Policy Compilation from Plans in Hybrid Probabilistic Domains''}
      \begin{itemize}
        \item Extends from discrete states to continues
        \item Like \texttt{RFF} but additional heuristics and usage of \texttt{Metric-FF}
      \end{itemize}
  \end{itemize}

\begin{frame}
  \frametitle{Planning under uncertainty: FF-Replan vs. RFF}

  \begin{itemize}
    \item
  \end{itemize}
\end{frame}
